Höglinger et al. 2017

### 2025-02-20 IndividualStudies/DH_2017.qmd
Spent forever tweaking venn and table for dh_2017, now done

---
title: "Höglinger et al. 2017"
subtitle: "Trifunctional lipid probes for comprehensive studies of single lipid species in living cells"
format:
  html:
    embed-resources: false
standalone: false
---
<!-- R setup, reading data tables, wrangling data -->
```{r setup, echo=FALSE, include=FALSE}

@@

#### Heat map
:::{.border}
```{r, echo=FALSE, fig.height=10}

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE, height = 5}

# Ensure the data is in the correct format
DH_2017_data <- as.data.frame(DH_2017_data)
rownames(DH_2017_data) <- DH_2017_data[,1]
DH_2017_data[,1] <- NULL

Sph_proteins <- DH_2017_data |>
  filter(PSM_Sph > 0) |>
  select(PSM_Sph)

FA_proteins <- DH_2017_data |>
  filter(PSM_FA > 0) |>
  select(PSM_FA)

DAG_proteins <- DH_2017_data |>
  filter(PSM_DAG > 0) |>
  select(PSM_DAG)

@@

ggvenn(combined_venn_proteins)

>>>>

---
title: "Höglinger et al. 2017"
subtitle: "Trifunctional lipid probes for comprehensive studies of single lipid species in living cells"
format:
  html:
    embed-resources: false
standalone: false
---
<!-- R setup, reading data tables, wrangling data -->
```{r setup, echo=FALSE, include=FALSE, warning=FALSE}

@@

#### Heat map
:::{.border}
```{r, echo=FALSE, fig.height=10, warning=FALSE}

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE, width = 8}

# Ensure the data is in the correct format
DH_2017_data_AddingRownames <- as.data.frame(DH_2017_data)
rownames(DH_2017_data_AddingRownames) <- DH_2017_data_AddingRownames[,1]
DH_2017_data_AddingRownames[,1] <- NULL

Sph_proteins <- DH_2017_data_AddingRownames |>
  filter(PSM_Sph > 0) |>
  select(PSM_Sph)

FA_proteins <- DH_2017_data_AddingRownames |>
  filter(PSM_FA > 0) |>
  select(PSM_FA)

DAG_proteins <- DH_2017_data_AddingRownames |>
  filter(PSM_DAG > 0) |>
  select(PSM_DAG)

@@

ggvenn <- ggvenn(combined_venn_proteins,
                      show_percentage = FALSE,
                      show_elements = FALSE,
                      fill_color = c("orange", "purple", "blue")) +
        labs(x = "", y = "") +
        theme_minimal()

ggvenn

```

```{r, echo=FALSE, warning=FALSE}

DH_2017_data <- DH_2017_data |>
  mutate(VennRegion = case_when(
    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to all probes",
    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA == 0) ~ "Enriched to Sph only",
    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to DAG only",
    (PSM_Sph == 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to FA only",
    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to Sph and DAG",
    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to Sph and FA",
    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to DAG and FA"))

DH_2017_data$VennRegion <- factor(pull(DH_2017_data, VennRegion), ordered = TRUE, levels = c("Enriched to Sph only", "Enriched to DAG only", "Enriched to FA only", "Enriched to Sph and DAG", "Enriched to Sph and FA", "Enriched to DAG and FA", "Enriched to all probes"))

DH_2017_data_reactive <- crosstalk::SharedData$new(DH_2017_data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "Overlap",
                  label = "Select overlap regions to see co-enriched proteins:",
                  sharedData = DH_2017_data_reactive,
                  group = ~VennRegion,
                  inline = TRUE)
)

## Displays the reactive dataframe
datatable(DH_2017_data_reactive, options = list(pageLength = 20))

```
